LAs_clusters

### 2020-09-11 src/LAs_Clusters.Rmd
minor changes

data <- merge(data, ns, all.x = T)
data$south <- ifelse(is.na(data$south),0, data$south)
```

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          covariate.labels=c("pop. 16-64, 2018",
                             "pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of dministrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data)))))

>>>>

data <- merge(data, ns, all.x = T)
data$south <- ifelse(is.na(data$south),0, data$south)

# NOT RUN
# export file for future reference / backup
# data.out.path <- paste0(path, "/data/temp/data_for_aux.csv")
# write.csv(data, data.out.path)
```

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c("pop. 16-64, 2018",
                             "pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of dministrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data)))))
